Parsing Postfix log files

### 2009-04-07 doc/logparser-results.tex
Removed perfect worst and reverse ordering from the oracle section.

XXX SHOULD I BOTHER WITH PERFECT WORST\@?

Optimal rule ordering, as described in \sectionref{rule ordering for
efficiency}, is the best rule ordering it is possible to achieve without
having an oracle that magically divines which rule should be used to
recognise each log line.  Such an oracle would give perfect performance,
because only one rule needs to be used to recognise each log line.
\parsername{} can save a list showing which rule recognised each log line,
and use that list to simulate having an oracle and improve parsing speed
the second time a log file is parsed.   This does not provide a practical
benefit, but it does provide a means to evaluate the performance of optimal
rule ordering in comparison to an oracle.  The knowledge can also be used
to generate a perfect worst oracle, where every rule (subject to rule
conditions) is used before the correct rule.

\Graphref{Parsing time relative to shuffled ordering including perfect best
and worst graph} shows the parsing times of the perfect best and perfect
worst oracles, and the optimal and reverse orderings relative to shuffled
ordering; \tableref{Parsing time relative to shuffled ordering, including
oracles table} shows mean and standard deviation.  As expected, the perfect
best oracle is more efficient than optimal ordering, and likewise the
perfect worst oracle is less efficient than reverse ordering.
\Graphref{Percentage increase in parsing time when using optimal ordering
instead of perfect best oracle graph} and \graphref{Percentage decrease in
parsing time when using reverse ordering instead of perfect worst oracle
graph} show the percentage increase and decrease in parsing time when
using, respectively, optimal ordering instead of the perfect best oracle,
and reverse ordering instead of the perfect worst oracle; mean and standard
deviation are given for different groups of log files in
\tableref{Percentage increase in parsing time when using optimal ordering
instead of perfect best oracle table} and \tableref{Percentage decrease in
parsing time when using reverse ordering instead of perfect worst oracle
table}.

Once again, the difference between the oracles and optimal or reversed
orderings at its lowest when parsing log files resulting from a mail loop
(log files 22 \& 62--68), because the average number of rules tried per log
line is lower (see \graphref{Average number of rules tried per log line}).
The performance when parsing the first log file is different to the
remainder of the non-mail loop log files, because the hits field of every
rule is zero; optimal ordering is less efficient, and reverse ordering is
less inefficient.

@@

\showgraph{build/graph-perfect-best-and-perfect-worst-and-optimal-and-reverse-vs-shuffled}{Parsing
time relative to shuffled ordering, including oracles}{Parsing time
relative to shuffled ordering including perfect best and worst graph}

\showtable{build/include-perfect-best-and-optimal-and-reverse-and-perfect-worst-vs-shuffle}{Parsing
time relative to shuffled ordering, including oracles}{Parsing time
relative to shuffled ordering, including oracles table}

@@

\showgraph{build/graph-perfect-worst-vs-reverse}{Percentage decrease in
parsing time when using reverse ordering instead of perfect worst
oracle}{Percentage decrease in parsing time when using reverse ordering
instead of perfect worst oracle graph}

\showtable{build/include-perfect-worst-vs-reverse-stddev}{Percentage
decrease in parsing time when using reverse ordering instead of perfect
worst oracle}{Percentage decrease in parsing time when using reverse
ordering instead of perfect worst oracle table}

@@

>>>>

Optimal rule ordering, as described in \sectionref{rule ordering for
efficiency}, is the best rule ordering it is possible to achieve without
having an oracle that magically divines which rule should be used to
recognise each log line.  Such an oracle would give perfect performance,
because only one rule needs to be used to recognise each log line.
\parsername{} can save a list showing which rule recognised each log line,
and use that list to simulate an oracle and improve parsing speed the
second time a log file is parsed.  This does not provide a practical
benefit, but it does provide a means to evaluate the performance of optimal
rule ordering in comparison to an oracle.

\Graphref{Parsing time of perfect best oracle and optimal ordering relative
to shuffled ordering graph} shows the parsing times of the perfect best
oracle and the optimal ordering, relative to shuffled ordering;
\tableref{Parsing time of perfect best oracle and optimal ordering relative
to shuffled ordering table} shows mean and standard deviation.  As
expected, the perfect best oracle is more efficient than optimal ordering.
\Graphref{Percentage increase in parsing time when using optimal
ordering instead of perfect best oracle graph} shows the percentage
increase in parsing time when using optimal ordering instead of the perfect
best oracle; mean and standard deviation are given for different groups of
log files in \tableref{Percentage increase in parsing time when using
optimal ordering instead of perfect best oracle table}.

Once again, the difference between the perfect best oracle and optimal
ordering is at its lowest when parsing log files resulting from a mail loop
(log files 22 \& 62--68), because the average number of rules tried per log
line is lower (see \graphref{Average number of rules tried per log line}).
The performance of optimal ordering when parsing the first log file is much
worse than the remainder of the log files, because the hits field of every
rule is zero, so optimal ordering performs similarly to shuffled ordering
for that log file.

@@

\showgraph{build/graph-perfect-best-and-optimal-vs-shuffled}{Parsing time
of perfect best oracle and optimal ordering relative to shuffled
ordering}{Parsing time of perfect best oracle and optimal ordering relative
to shuffled ordering graph}

\showtable{build/include-perfect-best-and-optimal-vs-shuffle}{Parsing time
of perfect best oracle and optimal ordering relative to shuffled
ordering}{Parsing time of perfect best oracle and optimal ordering relative
to shuffled ordering table}

@@

@@

\showgraph{build/graph-percentage-time-spent-recognising-log-lines}{XXX}{XXX}
